A Logistic Regression Approach to CoIL Challenge 2000

### 2019-12-06 final project/Draft.Rmd
More work on draft

```{r setup, include = FALSE}
# Documentation at https://crsh.github.io/papaja_man/
# If you have no use for TeX beyond rendering R Markdown documents, I recommend you use TinyTex.
# install.packages("tinytex")
# tinytex::install_tinytex()
if (!"papaja" %in% rownames(installed.packages())) {
  devtools::install_github("crsh/papaja")
}
library("papaja")
library(kableExtra)
library(tidyverse)
library(pander)
library(gridExtra)
library(corrplot)
library(ggmosaic)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

  print(p)
}
```

### Numeric
```{r, echo=FALSE}
numeric_vars <- df %>%
  select(-CARAVAN, -MOSTYPE, -MGEMLEEF, -MOSHOOFD, -MGODRK, -PWAPART, -var) %>%
  names()

@@

```

@@

pander(data_dictionary)
```

>>>>

```{r setup, include = FALSE}
# Documentation at https://crsh.github.io/papaja_man/
# If you have no use for TeX beyond rendering R Markdown documents, I recommend you use TinyTex.
# install.packages("tinytex")
# tinytex::install_tinytex()
if (!"papaja" %in% rownames(installed.packages())) {
  devtools::install_github("crsh/papaja")
}
library("papaja")
library(kableExtra)
library(tidyverse)
library(pander)
library(gridExtra)
library(corrplot)
library(ggmosaic)
library(wesanderson)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

  print(p)
}
df <- df %>% select(-var)
```

### Numeric

```{r, echo=FALSE}
numeric_vars <- df %>%
  select(-CARAVAN, -MOSTYPE, -MGEMLEEF, -MOSHOOFD, -MGODRK, -PWAPART) %>%
  names()

@@

df <- df %>% select(-var)
```

Here is a correlation heatmap.  Although you can't see the variable names, you get a general sense of how they are correlated:

```{r, echo=FALSE}
pal <- wes_palette("Zissou1", 100, type = "continuous")

correlation_data <- df %>%
  select(-MOSTYPE, -MGEMLEEF, -MOSHOOFD, -MGODRK, -PWAPART) %>%
  mutate(CARAVAN = as.numeric(as.character(CARAVAN)))

correlation_matrix <- round(cor(correlation_data),2) %>%
  as.data.frame() %>%
  rownames_to_column("Var1") %>%
  gather(Var2, Correlation, -Var1) %>%
  arrange(Var1, Var2)

correlation_matrix$Var2 <- factor(correlation_matrix$Var2,levels=rev(unique(correlation_matrix$Var2)))

ggplot(correlation_matrix, aes(x=Var1, y=Var2, fill=Correlation)) + 
  geom_tile() +
  scale_fill_gradientn(colours = pal) +
   theme(axis.title.x=element_blank(),
         axis.text.x=element_blank(),
         axis.ticks.x=element_blank(),
         axis.title.y=element_blank(),
         axis.text.y=element_blank(),
         axis.ticks.y=element_blank())
```

Most of the correlation heatmap is yellow which is has a correlation coeffient of zero.  Here's a density plot of the correlation coefficients:

```{r, echo=FALSE}
ggplot(correlation_matrix, aes(Correlation)) +
  geom_density(fill="red", color="red")
```

@@

data_dictionary %>%
  arrange(Name) %>%
  pander()
```
